---
title: "Homework 2"
author: "RuiJun Chen"
date: "10/2/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
```

## Problem 1
```{r}
#Read in Mr. Trash Wheel, omitting non-data entries and rows without dumpster-specific data, then rounding sports balls to integers
trash_data = 
  read_excel(
    "./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx", 
    range = "A2:N370") %>% 
  janitor::clean_names() %>% 
  drop_na(dumpster) %>% 
  mutate(sports_balls = as.integer(sports_balls))

```

```{r}
#Read in 2017 precipitation data excluding rows without precipitation data and adding year
precip2017_data = 
  read_excel(
    "./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx", 
    sheet = "2017 Precipitation",
    range = "A2:B14") %>% 
  janitor::clean_names() %>% 
  mutate(year = 2017)

#Read in 2018 precipitation data excluding rows without precipitation data and adding year
precip2018_data = 
  read_excel(
    "./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx", 
    sheet = "2017 Precipitation",
    range = "A2:B14") %>% 
  janitor::clean_names() %>% 
  mutate(year = 2018)

#Combine precipitation datasets and convert month to characters
combined_precip = 
  bind_rows(precip2017_data, precip2018_data) %>% 
  mutate(month = month.name[month])
```

The Mr. Trash Wheel database shows that there are a total of `r trash_data %>% count() %>% pull(n)` observations and `r trash_data %>% pull(dumpster) %>% last()` dumpsters which collected trash between `r trash_data %>% pull(month) %>% first()` `r trash_data %>% pull(year) %>% first()` and `r trash_data %>% pull(month) %>% last()` `r trash_data %>% pull(year) %>% last()`. In total, Mr. Trash Wheel collected `r trash_data %>% pull(weight_tons) %>% sum()` tons of trash with a volume of `r trash_data %>% pull(volume_cubic_yards) %>% sum()` in cubic yards. The median number of sports balls pulled from dumpsters in 2017 was `r trash_data %>% filter(year==2017) %>% pull(sports_balls) %>% median()`. In terms of precipitation in 2017 and 2018 combined, there were a total of `r combined_precip %>% count() %>% pull(n)` observations with a total precipitation of `r combined_precip %>% filter(year==2017) %>% pull(total) %>% sum()` in 2017 and total precipitation of `r combined_precip %>% filter(year==2018) %>% pull(total) %>% sum()` in 2018. 

## Problem 2
```{r}
#Read in pols-month.csv and clean
pols = 
  read_csv("./data/pols-month.csv") %>% 
  janitor::clean_names() %>% 
  separate(mon, into = c("year", "month", "day"), sep = "-", convert = TRUE) %>% 
  mutate(month = month.name[month]) %>% 
  mutate(president = if_else(prez_gop==1, "gop", "dem")) %>% 
  select(-prez_gop, -prez_dem, -day)
```

```{r}
#Read in snp.csv and clean
snp = 
  read_csv("./data/snp.csv") %>% 
  janitor::clean_names() %>% 
  separate(date, into = c("month", "day", "year"), sep = "/", convert = TRUE) %>% 
  mutate(month = month.name[month]) %>% 
  select(-day) %>% 
  arrange(year, month) %>% 
  select(year, month, everything())
```

```{r}
#Read in unemployment.csv and tiday to long format with same variable names/formats
unemployment = 
  read_csv("./data/unemployment.csv") %>% 
  pivot_longer(Jan:Dec, names_to = "month", values_to = "unemployment_rate") %>% 
  mutate(month = month.name[match(month, month.abb)]) %>% 
  janitor::clean_names() %>% 
  arrange(year, month)
```

```{r}
#Merge snp into pols then merge unemployment into result
pol_data = 
  full_join(pols, snp, by = c("year", "month")) %>% 
  full_join(unemployment, by = c("year", "month"))
```
The pols-month dataset contained data on the number of positions Democrats and Republicans held in Congress, as governors, or as the President, spanning from `r pols %>% pull(month) %>% first()` `r pols %>% pull(year) %>% first()` to `r pols %>% pull(month) %>% last()` `r pols %>% pull(year) %>% last()`. The snp dataset contained the closing value of the S&P index for each month, spanning from `r snp %>% pull(month) %>% first()` `r snp %>% pull(year) %>% first()` to `r snp %>% pull(month) %>% last()` `r snp %>% pull(year) %>% last()`. The unemployment dataset contained the unemployment rate for each month, spanning from `r unemployment %>% pull(month) %>% first()` `r unemployment %>% pull(year) %>% first()` to `r unemployment %>% pull(month) %>% last()` `r unemployment %>% pull(year) %>% last()`. The final dataset had dimensions of `r pol_data %>% dim_desc()`, with data spanning from `r pol_data %>% pull(month) %>% first()` `r pol_data%>% pull(year) %>% first()` to `r pol_data %>% pull(month) %>% last()` `r pol_data %>% pull(year) %>% last()` and variables of `r pol_data %>% tbl_vars()`.

## Problem 3